---
title: "An Interactive Map of Publicly-Funded Cultural Institutions in Berlin"
author: "Graham Booth"
date: "10/25/2021"
output: html_document
---

```{r setup, include=FALSE}

#Host your webpage on either GitHub Pages, RPubs, or NeoCities.

knitr::opts_chunk$set(echo = TRUE)
```

This web page was created using RStudio and the Leaflet and was my Week 2 assignment submission for the Developing Data Products course of the Coursera/John Hopkins University Data Science Specialisation.

The map below shows the locations of funded cultural institutions within Berlin. It uses a dataset that can be found on the Berlin Open Data website [here](https://daten.berlin.de/datensaetze/standorte-geförderter-kultureinrichtungen) and is free to share and adapt under the following [creative commons license](https://creativecommons.org/licenses/by/3.0/de/).

The map can be zoomed with the mouse or using the + and - icons, to better differentiate the data. The different icon types and colour used on the markers refer to different categories of cultural institution, of which there are ten in total. Hovering over a given marker reveals a pop-up, which shows the name of the institution (in German) and the closest public transport station (underground or suburban train).

```{r, echo=FALSE, message=FALSE}
library("readxl")
library("dplyr")
library("leaflet")

if (!file.exists("cultural_institutions.xlsx")) {
download.file("http://www.berlin.de/sen/kultur/_assets/statistiken/kultureinrichtungen_alle.xlsx", "cultural_institutions.xlsx") }

cultural_institutions <- read_excel("cultural_institutions.xlsx") %>% 
  mutate(Lat = as.numeric(Lat)) %>%
  mutate(Lon = as.numeric(Lon)) %>%
  mutate(GruppeA = as.factor(GruppeA)) %>%
  mutate(icon = case_when(
    GruppeA == "Archive/Bibliotheken" ~ 'pencil',
    GruppeA == "Berliner Landesmuseen" ~ 'university',    
    GruppeA == "Bildende Kunst" ~ 'paint-brush',
    GruppeA == "Bühnen und Theater" ~ 'ticket',
    GruppeA == "Förderung" ~ 'shopping-cart',
    GruppeA == "Gedenkstätten" ~ 'shield',
    GruppeA == "Literatur und Kino" ~ 'film',
    GruppeA == "Opern und Chöre" ~ 'bell',
    GruppeA == "Preußische Schlösser & Gärten" ~ 'tree',
    GruppeA == "Staatliche Museen zu Berlin / Stiftung Preußischer Kulturbesitz" ~ 'building'
    )
  ) %>%
  mutate(icon_colour = case_when(
    GruppeA == "Archive/Bibliotheken" ~ 'red',
    GruppeA == "Berliner Landesmuseen" ~ 'lightblue',    
    GruppeA == "Bildende Kunst" ~ 'blue',
    GruppeA == "Bühnen und Theater" ~ 'yellow',
    GruppeA == "Förderung" ~ 'orange',
    GruppeA == "Gedenkstätten" ~ 'brown',
    GruppeA == "Literatur und Kino" ~ 'purple',
    GruppeA == "Opern und Chöre" ~ 'pink',
    GruppeA == "Preußische Schlösser & Gärten" ~ 'green',
    GruppeA == "Staatliche Museen zu Berlin / Stiftung Preußischer Kulturbesitz" ~ 'white'
  )
)

my_map <- leaflet() %>% 
  addTiles() %>%
  addAwesomeMarkers(
    lat=cultural_institutions$Lat,
    lng=cultural_institutions$Lon,
    label=paste(cultural_institutions$Institution, "-", cultural_institutions$SUBahn),
    icon=awesomeIcons(icon = cultural_institutions$icon, markerColor = cultural_institutions$icon_colour, library = 'fa')
  )
my_map
```